\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Model Engineering College Ernakulam \linebreak 
Department of Computer Science \& Engineering \linebreak
B.Tech. Computer Science \& Engineering \linebreak
CS 6A Project Design \linebreak
Project Proposal \linebreak
THE HELP}

\author{41.Peter Joseph \and 42.Pranoy Paul \and 55.Siddarth M \and 57.Stamley Johnson}





\begin{document}

\maketitle



\section{Introduction}

The project aims at providing people the luxury to search and find the perfect domestic help in the country.
It provides a platform that showcases an array of attributes, skills and authenticity of various profiles for candidates recruited for the domestic help.
It is the perfect solution for the public's need for domestic help. 

\section{Proposed Project}

The help.\\
Initially proposed to be a website and can later be considered for android app development. 
The website is to have profiles for the candidates recruited. 
A recruitment process can be fully completed only by proper verification by the team. A background check if possible has to be carried out before displaying it in
the website.\\
Once the verification process is complete, the profiles are then showcased on the website along with their skill sets. 
The user gets the chance to search and find the perfect candidate for the work at hand. 
The user can book the candidate and a request can be sent to the candidate who has the freedom to accept it or reject it.\\
It is mandatory for the user to create an account for utilising the website fully. 
It is also mandatory for the user to provide a feedback or a rating to the candidate once his work is done. This helps the candidate profiles.\\ \\
How candidates make money ?\\
By getting paid for the amount of work done and not by a fixed price.

\subsection{Problem Statements}

There exists no proper system which deals with the issue of finding the perfect domestic help that considers both the authenticity and the quality of the work done.

\subsection{Problem Solution}

A website or an application can be developed which can act in favour of both the public and the cadidates. 
The general public is provided with the opportunity to search and choose their perfect domestic help by taking into consideration all their work requirements. 
The candidates get the chance to showcase their skill set to the public through a single portal and also maintains the authenticity of their profiles. 


\subsection{Hardware \& Software Requirements}

\begin{itemize}
\item Laptop
\item Phone
\item Django
\item MySql
\item Miktex
\item CSS
\item HTML
\item JavaScript
\end{itemize}

We are in possession of the above mentioned requirements and they are all legally permitted to be used.

\subsection{Work Schedule}


\begin{center}
\begin{tabular}{ |c|c| } 
 \hline
 Week & Work to be compiled \\  \hline
 1 & Requirement Specification \\  \hline
 2 & Basic Layout of Website\\  \hline
 3 & Database Design\\  \hline
 4 & Creating User Profiles\\  \hline
 5 & Login and Signup\\  \hline
 6 & Search Algorithm Implementation\\  \hline
 7 & Integration and Testing\\  \hline
 8 & Project Review\\  \hline
 \hline
\end{tabular}
\end{center}






\end{document}