\documentclass[twocolumn,10pt]{article}
\oddsidemargin 0.1in
\addtolength{\oddsidemargin}{-.4in}
\addtolength{\textwidth}{1in}
\addtolength{\textheight}{2in}
\addtolength{\headheight}{-1in}
\title{Model Engineering College Ernakulam
\\Department of Computer Science \& Engineering
\\B. Tech. Computer Science \& Engineering (Image Processing)
\\CS 17L3 Project Design
\\ Project Proposal
%\\ An Approach to Enhance Contrast and Brightness Of Low Contrast Images Using Adaptive Gamma Correction and Cumulative Distribution Function
\\proposed project name
}

\author{rollno admissionno name}
\usepackage{epsfig}
\begin{document}

\maketitle
	
{\bf Keywords:}
list of keywords\\
\abstract{} 
type your abstract here
%%............................................................................................
\section{\label{intro}Introduction}
\section{\label{work}Report of Work Done}
\subsection{Literature Survey Report}

\subsection{System Study Report}
\section{Proposed Project}
describe your proposed project in detail
\subsection{\label{ps}Problem Statement}
This should clearly, without any scope for differing interpretations later, state the aim of the project.

\subsection{Proposed Solution}
This should clearly, without any scope for differing interpretations later, state the methods you are suggesting to achieve the result.
\subsection{Hardware \& Software Requirements}
Specify the requirements. State whether you own them. If it is in the college/institute
 where exactly. If the required items are not available straightaway, state, how do you propose to make them available. 
Ensure that all the hardware/software used are legally permitted for the purpose.

\subsection{Work Schedule}
describe tentative work schedule



\begin{thebibliography}{999}
\addcontentsline{toc}{chapter}{References}

\end{thebibliography}

\hrule
\vspace{.5in}
%
%External Guide \\
%\vspace{.5in}
Internal Guide:\\
name \\
designation \\
Department of Computer Science \& Engineering \\
Model Engineering College \\

\end{document}
